Home Nighttime Cough Monitoring

### 2025-02-26 Angela Metcalf/quantifying_cl_cf_carriers.qmd
mostly file path changes

---
title: "Quantifying Sweat Chloride in CF Carriers"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Documents/Miscellaneous/zotero.bib
csl: /Users/timvigers/GitHub/styles/american-medical-association.csl
editor: source
---

```{r setup}
#| include: false
library(tidyverse)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/timvigers/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Angela Metcalf/Quantifying Sweat Chloride in CF Carriers")
```

```{r data cleaning}
#| message: false
df <- read.csv("./Data_Raw/Midpoint data.csv", na.strings = "")
df <- df %>%
  mutate(
    `Right Arm Cl` = as.numeric(Sweat.chloride..right.arm),
    `Left Arm Cl` = as.numeric(Sweat.chloride..left.arm),
    `Right Arm Na` = as.numeric(Sweat.sodium..right.arm),
    `Left Arm Na` = as.numeric(Sweat.sodium..left.arm)
  )
df$`Mean Cl` <- rowMeans(df[, c("Right Arm Cl", "Left Arm Cl")])
df$`Mean Na` <- rowMeans(df[, c("Right Arm Na", "Left Arm Na")])
```

# Plots

```{r}
ggplot(df,aes(y=`Mean Cl`))+boxplot()
```

>>>>

---
title: "Quantifying Sweat Chloride in CF Carriers"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /home/timvigers/Documents/Miscellaneous/zotero.bib
csl: /home/timvigers/Documents/GitHub/styles/american-medical-association.csl
editor: source
---

```{r setup}
#| include: false
library(redcapAPI)
library(tidyverse)
library(arsenal)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/timvigers/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = "/home/timvigers/OneDrive/Vigers/CF/Angela Metcalf/Quantifying Sweat Chloride in CF Carriers")
```

```{r data cleaning}
#| message: false
# Import from REDCap
# unlockREDCap(c(rcon = "Sweat Electrolytes in CF Carriers 24-0691"),
#   keyring = "API_KEYs",
#   envir = 1,
#   url = "https://redcap.ucdenver.edu/api/"
# )
# df <- exportRecordsTyped(rcon)
# # Format
# df <- df %>%
#   mutate(
#     `Cl Right` = as.numeric(cl_right), `Cl Left` = as.numeric(cl_left),
#     `Na Right` = as.numeric(na_right), `Na Left` = as.numeric(na_left)
#   )
# df$`Mean Cl` <- rowMeans(df[, c("Cl Right", "Cl Left")])
# df$`Mean Na` <- rowMeans(df[, c("Na Right", "Na Left")])
```

# Confidence interval power calculations

```{r}
ns <- 35:45
power <- lapply(ns, function(n) {
  se <- qt(0.05 / 2, lower.tail = F, df = n - 1) * (12 / sqrt(n))
  return(c(
    "Confidence level" = 0.95, "Sample size (N)" = n,
    "Actual Distance from Mean to Limits" = se,
    "Standard deviation of sweat chloride" = 12
  ))
})
power <- do.call(rbind, power)
knitr::kable(power)
```

### 2025-02-26 Christine Chan/CF Registry/cf_registry_survival_analysis.qmd
mostly file path changes

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(knitr)
library(eulerr)
library(broom)
library(emmeans)
library(ggstats)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry")
```

>>>>

```{r}
#| include: false
library(Hmisc)
library(zoo)
library(tidyverse)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(survival)
library(survminer)
library(knitr)
library(eulerr)
library(broom)
library(emmeans)
library(ggstats)
knitr::opts_knit$set(root.dir = "/home/timvigers/OneDrive/Vigers/CF/Christine Chan/CF Registry")
```

### 2025-02-26 Christine Chan/EnVision CF/christine_CGM_OGTT_category.qmd
mostly file path changes

```{r setup}
#| include: false
library(gtsummary)
library(dplyr)
library(pracma)
library(ggplot2)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/tim/OneDrive/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}
# Import
df <- read.csv("./Christine Chan/EnVision CF/Data_Clean/analysis_dataset.csv",
  na.strings = ""
)
# Filter out those with no CGM data and those with no associated OGTT
df <- df %>% filter(!is.na(mean_sensor), !is.na(Date))
# Scully cutoffs
df$scully140 <- cut(df$percent_time_over_140,
  breaks = c(-Inf, 17.5, Inf), right = F
)
df$scully180 <- cut(df$percent_time_over_180,
  breaks = c(-Inf, 3.4, Inf), right = F
)
```

@@

```{r}
#| label: tbl-1
#| tbl-cap: Participant characteristics (overall)
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    redcap_data_access_group, age_visit:origin_race, cftr_mutation_1,
    cftr_mutation_2, weight
  ) %>%
  tbl_summary(by = redcap_data_access_group, missing_text = "Missing") %>%
  add_overall()
```

@@

```{r}
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    redcap_data_access_group, age_visit:origin_race, cftr_mutation_1,
    cftr_mutation_2, weight, scully140
  ) %>%
  tbl_summary(by = scully140, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```

@@

```{r}
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    redcap_data_access_group, age_visit:origin_race, cftr_mutation_1,
    cftr_mutation_2, weight, scully180
  ) %>%
  tbl_summary(by = scully180, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```

>>>>

```{r setup}
#| include: false
library(gtsummary)
library(dplyr)
library(pracma)
library(ggplot2)
knitr::opts_knit$set(root.dir = "/home/timvigers/OneDrive/Vigers/CF")
```

```{r data cleaning}
# Import
df <- read.csv("./Christine Chan/EnVision CF/Data_Clean/envision_analysis_dataset.csv",
  na.strings = ""
)
# Filter out those with no CGM data and those with no associated OGTT
df <- df %>% filter(!is.na(mean_sensor), !is.na(Date))
# Scully cutoffs
df$scully140 <- cut(df$percent_time_over_140,
  breaks = c(-Inf, 17.5, Inf), right = F
)
df$scully180 <- cut(df$percent_time_over_180,
  breaks = c(-Inf, 3.4, Inf), right = F
)
```

@@

```{r}
#| label: tbl-1
#| tbl-cap: Participant characteristics (overall)
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    redcap_data_access_group, age_visit:origin_race, CFTR, weight
  ) %>%
  tbl_summary(by = redcap_data_access_group, missing_text = "Missing") %>%
  add_overall()
```

@@

```{r}
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    redcap_data_access_group, age_visit:origin_race, CFTR, weight, scully140
  ) %>%
  tbl_summary(by = scully140, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```

@@

```{r}
df %>%
  group_by(study_id) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(
    redcap_data_access_group, age_visit:origin_race, CFTR, weight, scully180
  ) %>%
  tbl_summary(by = scully180, missing_text = "Missing") %>%
  add_p() %>%
  separate_p_footnotes() %>%
  add_overall()
```

### 2025-02-26 Edith Zemanick/Sweat Variability/sweat_test_analysis_chec.qmd
mostly file path changes

---
title: "CHEC Study Sweat Chloride"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    fig-width: 9
    fig-height: 7
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /home/timvigers/Documents/Miscellaneous/zotero.bib
csl: /home/timvigers/GitHub/styles/american-medical-association.csl
editor: source
execute:
  warning: false
---

@@

```{r}
model_df <- chec_long %>%
  select(subject, cl, na, ratio, pre_post) %>%
  drop_na()
m <- lmer(cl ~ pre_post * na + (1 | subject), data = model_df)
# From Amalia
m1 <- glm(pre_post ~ cl, data = model_df, family = "binomial")
m2 <- glm(pre_post ~ cl + na, data = model_df, family = "binomial")
m3 <- glm(pre_post ~ cl * na, data = model_df, family = "binomial")
m4 <- glm(pre_post ~ ratio, data = model_df, family = "binomial")
gt(compare_performance(m1, m2, m3, m4, metrics = "common")) %>%
  fmt_number(decimals = 3)
model_df$m1_pred <- factor(predict(m1, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m2_pred <- factor(predict(m2, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m3_pred <- factor(predict(m3, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m4_pred <- factor(predict(m4, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
```

>>>>

---
title: "CHEC Study Sweat Chloride"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    fig-width: 9
    fig-height: 7
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /home/timvigers/Documents/Miscellaneous/zotero.bib
csl: /home/timvigers/Documents/GitHub/styles/american-medical-association.csl
editor: source
execute:
  warning: false
---

@@

```{r}
model_df <- chec_long %>%
  select(subject, cl, na, ratio, pre_post) %>%
  drop_na()
m <- lmer(cl ~ pre_post * na + (1 | subject), data = model_df)
# From Amalia
m1 <- glm(pre_post ~ cl, data = model_df, family = "binomial")
m2 <- glm(pre_post ~ cl + na, data = model_df, family = "binomial")
m3 <- glm(pre_post ~ cl * na, data = model_df, family = "binomial")
m4 <- glm(pre_post ~ scale(ratio), data = model_df, family = "binomial")
gt(compare_performance(m1, m2, m3, m4, metrics = "common")) %>%
  fmt_number(decimals = 3)
model_df$m1_pred <- factor(predict(m1, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m2_pred <- factor(predict(m2, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m3_pred <- factor(predict(m3, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
model_df$m4_pred <- factor(predict(m4, type = "response") > 0.5,
  levels = c(F, T), labels = c("pred_pre", "pred_post")
)
```

### 2025-02-26 Lilah Melzer/cough_monitor_analysis.qmd
mostly file path changes

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(tidyverse)
library(ggstats)
library(corrplot)
library(patchwork)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor")
```

>>>>

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(tidyverse)
library(ggstats)
library(corrplot)
library(patchwork)
knitr::opts_knit$set(root.dir = "/home/timvigers/OneDrive/Vigers/CF/Lilah Melzer/Lilah Cough Monitor")
```
